---
title: "model.prior.sensitivity.analysis"
author: "Ania Kawiecki"
date: "2023-08-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries}
library(pacman)
pacman::p_load(tidyverse, sf, lubridate, parallel, here)
```


## function that names the model and prior

```{r}
#' Assign identifiers for the model and the prior used to an INLA model 
#'
#' This function takes a list of INLA models as input and returns data frame of the fixed effects, the prior and an identifier for each model.
#'
#' @param m  A list of INLA models modified to include a "prior" and a "model" columns
#' @return A data frame of the fixed effects for each model.
#' 

fx.prior.names <- function(model.list, model.name, prior.name){
  
 lapply(1:length(model.list), function(x)
   append(model.list[[x]], c(model=model.name, prior=prior.name[[x]],m= paste("m", x, sep="." )) ))
}

```

## functions that extract prior and type of model into a data frame

```{r fx.fe.prior}

#' Extract fixed effect estimates and prior from model list 
#'
#' This function takes a list of INLA models as input and returns data frame of the fixed effects, the prior and an identifier for each model.
#'
#' @param m  A list of INLA models modified to include a "prior" and a "model" columns
#' @return A data frame of the fixed effects for each model.
#' 

fx.fe.prior <- function(m){
  
# f.fix.eff.exp extracts fixed effect from INLA model and names model 
f.fe.prior <- function(x){
  # exponentiates the model estimates to return them to the scale of the original count data
  round(exp(m[[x]][["summary.fixed"]]), digits = 2) %>% 
     #adds a column named "variable" with the the variable names (that are presented as rownames in the INLA results)
  rownames_to_column( var = "variable") %>% 
    # a value that lists the fixed effects in each model including the intercept
    mutate(fixed= paste(m[[x]][["names.fixed"]], collapse= "+"), 
            # a value that lists the fixed effects in each model without the intercept (added within in our model function, not an INLA result)
           fixed.s= m[[x]][["fixed.effect.s"]],
            # a value that identifies the model (added within in our model function, not an INLA result)
           model= m[[x]][["model"]], 
           # a value that identifies the prior used (added within in our model function, not an INLA result)
           prior= m[[x]][["prior"]]) %>% 
    # renames quantile column names from INLA results for easier use
    rename(q0.025 = "0.025quant", q0.5 = "0.5quant", q0.975 = "0.975quant") 
}

lapply(1:length(m), f.fe.prior) %>% bind_rows()

}


```

```{r fe.waic.prior}

#' Difference in WAIC and prior 
#'
#' This function takes a list of INLA models as input and returns their WAIC values and difference in WAIC compared to the lowest WAIC value and their priors
#'
#' @param m A list of INLA models modified to include a "prior" and a "model" columns
#' @return A data frame of the WAIC values and the WAIC rank of each model compared to the lowest WAIC.

fx.waic.prior <- function(m){
  #' Find model with lowest WAIC
  #'
  #' This function takes a list of INLA models as input and returns the model that has the lowest WAIC.
  #'
  #' @param m A list of INLA models.
  #' @return A model with the lowest WAIC from a list of models.
  f.waic.min <- function(m) {
    # find the lowest WAIC value among the models
    min.waic <- min(unlist(lapply(1:length(m), function(x) {
      # this function extracts the WAIC value from the INLA summary for each model
      m[[x]][["waic"]][["waic"]]
    })))

    # condition: is each model's WAIC the lowest WAIC?
    min.waic.T <- sapply(1:length(m), function(x) m[[x]][["waic"]][["waic"]] == min.waic)

    # select the model where the that model's WAIC is the lowest WAIC
    m.min.waic <- m[min.waic.T == TRUE]
  }
  
  m.min.waic <- f.waic.min(m)
  
  
  f.waic.compare <- function(x){
    
    n= length(m[[x]][["waic"]][["local.waic"]])
    
    waic.compare <- list( 
      # a value that identifies the model (added within in our model function, not an INLA result)
      model= m[[x]][["model"]], 
      # a value that identifies the prior used (added within in our model function, not an INLA result)
      prior= m[[x]][["prior"]],
      # a value that lists the fixed effects in each model
      fixed = c(paste(m[[x]][["names.fixed"]], collapse = "+")),
      # a value that lists the fixed effects in each model without the intercept (added within in our model function, not an INLA result)
      fixed.s = m[[x]][["fixed.effect.s"]],
      # a value that lists the random effects in each model
      random = c(paste(m[[x]][["model.random"]], collapse = "+")),
      # extract waic value from each model
      waic = m[[x]][["waic"]][["waic"]],
      # st. error of the point-wise waic
      s.e = as.numeric(sqrt(n * var(m[[x]][["waic"]][["local.waic"]], na.rm = TRUE))),
      # lower ci of the point-wise waic
      ci.l = m[[x]][["waic"]][["waic"]] - as.numeric(sqrt(n * var(m[[x]][["waic"]][["local.waic"]], na.rm = TRUE))) * 2.6,
      # upper ci of the point-wise waic
      ci.u = m[[x]][["waic"]][["waic"]] + as.numeric(sqrt(n * var(m[[x]][["waic"]][["local.waic"]], na.rm = TRUE))) * 2.6,
      # difference between each model's waic and the lowest waic
      d.mean.waic = m[[x]][["waic"]][["waic"]] - m.min.waic[[1]][["waic"]][["waic"]],
      # st. error of the difference between each model's waic and the lowest waic
      d.s.e = as.numeric(sqrt(n * var(m[[x]][["waic"]][["local.waic"]] - m.min.waic[[1]][["waic"]][["local.waic"]], na.rm = TRUE))),
      # lower ci of the difference between each model's waic and the lowest waic
      ci.d.l = m[[x]][["waic"]][["waic"]] - m.min.waic[[1]][["waic"]][["waic"]] - as.numeric(sqrt(n * var(m[[x]][["waic"]][["local.waic"]] - m.min.waic[[1]][["waic"]][["local.waic"]], na.rm = TRUE))) * 2.6,
      # upper ci of the difference between each model's waic and the lowest waic
      ci.d.u = m[[x]][["waic"]][["waic"]] - m.min.waic[[1]][["waic"]][["waic"]] + as.numeric(sqrt(n * var(m[[x]][["waic"]][["local.waic"]] - m.min.waic[[1]][["waic"]][["local.waic"]], na.rm = TRUE))) * 2.6,
      # prediction penalty
      p.waic = sum(m[[x]][["waic"]][["local.p.eff"]], na.rm = TRUE)
    )
    
  }
  
  df.model <-  lapply(1:length(m),f.waic.compare) %>% bind_rows() %>% arrange(waic) 

}
```


```{r data }

df <-  readRDS(here("analysis", "data", "derived_data", "variables", "variables_2014",  "vbles.space.decay.14.rds"))

```


#current model priors
Prior distributions for parameters were chosen based on considerations of weak information and parsimony, using the defaults proposed in the R-INLA documentation. We assumed zero- mean Gaussian prior distributions $\beta \sim Normal(0,1000)$ for all fixed effects (A and B) and log gamma prior distributions for the iid and RW1 random effects ($\eta_{i} \sim log gamma(1, 0.00005)$ and $\delta_{t} \sim log gamma(1, 0.00005)$). For the spatial random effect we implemented a penalized complexity (PC) prior with $range = c(10,0.01)$, and $\sigma = c(1, 0.01)$. PC priors are recommended, as they reward simplicity by shrinking parameter estimates toward a "base model,", thus preventing over-fitting (@simpson2015).

```{r mesh and spatial field}
## ----coordinates------------------------------------------------------------------------------------------------

# extract coordinates from data that will be used as vertices for the mesh

data.coord <- cbind(
  x = unlist(map(df$geometry, 1)),
  y = unlist(map(df$geometry, 2))
)

## ----create INLA mesh--------------------------------------------------------------------------------------------

# creates a polygon around the coordinates to allow smaller triangles inside polygon and larger triangles outside
# this saves computational power in the area with larger triangles
bnd <- inla.nonconvex.hull(data.coord, concave = 200)

#  mesh that allows discretization of the random field
mesh <- inla.mesh.2d(data.coord, boundary = bnd, max.edge = c(50, 100), cutoff = 20, min.angle = 30)

## ----projection A matrix---------------------------------------------------------------------------

# projection matrix A that projects the continuous Gaussian random field from the data points to the mesh nodes.
a1 <- inla.spde.make.A(mesh = mesh, loc = data.coord)


```


```{r pc priors for the spatial random effect}
## ----SPDE with PC priors---------------------------------------------------------------------------

# builds the SPDE model
spde <- inla.spde2.pcmatern(
  mesh = mesh,
  prior.range = c(10, 0.01), # the probability that the range is less than 10 (m) is 0.01
  prior.sigma = c(1, 0.01)
) # the probability that variance (on the log scale) is more that 1 is 0.01)

# make the index set for the SPDE model
sp.index <- inla.spde.make.index(
  name = "spatial.field", # name of the effect
  n.spde = spde$n.spde
) # number of vertices of the SPDE model


```

```{r best model for spray effects over time (mbest) }

# model that was selected as best representing the effect of sprays within household i (g20_day.max)
# with the original priors 

  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(g20_day.max= df[["g20_day.max"]], 
                     location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max + f(location_code, model ="iid")+ f(month, model ="rw1")+ f(spatial.field, model = spde)
m.t.0 <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )

 # we append 2 variables (model and prior) to the model result to identify the prior used and the model itself 
m.t.0.names <- append(m.t.0, c(model="time", prior="original"))

```


```{r best model for spray effects over space}

# model that had the lowest WAIC when representing the effect of sprays in neighboring households using the study data 
# with the original priors 

 stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(i_total= df[["i_total"]], 
                  g20_day.max= df[["g20_day.max"]],
                  location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max + i_total + f(location_code, model ="iid")+ f(month, model ="rw1")+ f(spatial.field, model = spde)
  

m.s.0 <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )

m.s.0.names <- append(m.s.0, c(model="space", prior="original"))
```


```{r list original models}
m.0 <- list(m.t.0.names, m.s.0.names)
```


# changing the priors


## spatial prior
For the spatial random effect we implemented a penalized complexity (PC) prior with $range = c(10,0.01)$, and $\sigma = c(1, 0.01)$. PC priors are recommended, as they reward simplicity by shrinking parameter estimates toward a "base model,", thus preventing over-fitting. 

*Alternative spatial priors*

try a range of 0.1 and of 100 
try a variance of 0.5 and of 3 

```{r list of spatial priors}

priors.spatial <- list(
spde.1 <- inla.spde2.pcmatern(mesh = mesh, 
                                prior.range = c(0.1,0.01),  # the probability that the range is less than 0.1 (m) is 0.01. The range here should be rather large (compare to the dataset extension) 
                                 prior.sigma = c(1, 0.01)),   # the probability that variance (on the log scale) is more that 1 is 0.01)
spde.2 <- inla.spde2.pcmatern(mesh = mesh, 
                                prior.range = c(100,0.01),  # the probability that the range is less than 100 (m) is 0.01. The range here should be rather large (compare to the dataset extension) 
                                 prior.sigma = c(1, 0.01)) ,  # the probability that variance (on the log scale) is more that 1 is 0.01), 

spde.3 <- inla.spde2.pcmatern(mesh = mesh, 
                                prior.range = c(10,0.01),  # the probability that the range is less than 100 (m) is 0.01. The range here should be rather large (compare to the dataset extension) 
                                 prior.sigma = c(0.5, 0.01)),   # the probability that variance (on the log scale) is more that 0.5 is 0.01), 
spde.4 <- inla.spde2.pcmatern(mesh = mesh, 
                                prior.range = c(10,0.01),  # the probability that the range is less than 100 (m) is 0.01. The range here should be rather large (compare to the dataset extension) 
                                 prior.sigma = c(3, 0.01))   # the probability that variance (on the log scale) is more that 1 is 0.01), 
)

priors.spatial.names.vector <-  c("spde.1", "spde.2", "spde.3", "spde.4")
```


Model fitting is done with the lapply() function so that each prior in list prior.list is used in turn:

```{r m.t.spatial}

m.t.spatial <- lapply(priors.spatial, function(spde) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  A = list(a1,1), 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(g20_day.max= df[["g20_day.max"]], 
                     location_code = df[["location_code"]], 
                     month= df[["month"]])),
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max + f(location_code, model ="iid")+ f(month, model ="rw1")+ f(spatial.field, model = spde)


m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )

c(m, spde.prior= spde)

})



m.t.spatial.names <- fx.prior.names(m.t.spatial,"time", priors.spatial.names.vector)

```

```{r m.s.spatial}

m.s.spatial <- lapply(priors.spatial, function(spde) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(i_total= df[["i_total"]], 
                  g20_day.max= df[["g20_day.max"]],
                  location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max + i_total + f(location_code, model ="iid")+ f(month, model ="rw1")+ f(spatial.field, model = spde)
  

m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )

c(m, spde.prior= spde)

})

m.s.spatial.names <- fx.prior.names(m.s.spatial,"space", priors.spatial.names.vector)

```


```{r output m.spatial, eval = FALSE}

m.spatial <- c( m.0, m.t.spatial.names, m.s.spatial.names)

m.spatial.fe <-  fx.fe.prior(m.spatial) 
m.spatial.waic <- fx.waic.prior(m.spatial)
```

## rw1 prior
We assumed log gamma prior distributions for the RW1 random effects ($\eta_{i} \sim log gamma(1, 0.00005)$ 

```{r simulate rw1, eval=FALSE}

# explore the response variable by month

# plot the AA_TOTAL by month 
rw1.plot <- ggplot(df, aes(x= month, y=AA_TOTAL))+
 geom_smooth(method="gam",formula=y~s(x,bs="cs",k=4), method.args=list(family=poisson))+geom_point(alpha=0.1)

rw1.plot 

# use inlatools to simulate different sigmas for the normal prior of rw1
rw1.1 <-inlatools::simulate_rw(sigma=0.1)

plot(inlatools::select_divergence(rw1.1),link="log")

rw1.2 <-inlatools::simulate_rw(sigma=0.25)

plot(inlatools::select_divergence(rw1.2),link="log")

rw1.3 <-inlatools::simulate_rw(sigma=0.5)

plot(inlatools::select_divergence(rw1.3),link="log")
```


```{r list of rw1 priors}

priors.rw1 <- list(
prior.rw1.1 <- list(prior="pc.prec",param=c(u=1,0.01)), # per recommedations of INLA documentaition for RW1 PC priors for poisson

#xi∼N(xi−1,σ2) with different sigmas
prior.rw1.2 <- list(prior="pc.prec",param=c(0.25,0.05)), #per simulations
prior.rw1.3 <- list(prior="pc.prec",param=c(0.5,0.05))  #per simulations
)

priors.rw1.names.vector <-  c("rw1.1", "rw1.2", "rw1.3")
```


```{r m.t.rw1}

m.t.rw1 <- lapply(priors.rw1, function(x) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(g20_day.max= df[["g20_day.max"]], 
                     location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max +
  f(location_code, model ="iid")+
  f(month, model ="rw1", 
    hyper=list( theta= x) )+
  f(spatial.field, model = spde)

  
m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )


})



m.t.rw1.names <- fx.prior.names(m.t.rw1,"time", priors.rw1.names.vector)

```

```{r m.s.rw1}

m.s.rw1 <- lapply(priors.rw1, function(x) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(i_total= df[["i_total"]], 
                  g20_day.max= df[["g20_day.max"]],
                  location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max + i_total +
  f(location_code, model ="iid")+ 
  f(month, model ="rw1", 
    hyper=list( theta= x) )+
  f(spatial.field, model = spde)
  

m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )

})

m.s.rw1.names <- fx.prior.names(m.s.rw1,"space", priors.rw1.names.vector)

```


## iid prior

Used vignette form https://inlatools.netlify.app/articles/prior as a guide.

We assumed log gamma prior distributions for the iid random effects $\delta_{t} \sim log gamma(1, 0.00005)$)


```{r simulate iid, eval=FALSE}
df.sum <- df %>% 
  group_by(location_code) %>% 
  summarise(sd= sd(AA_TOTAL))

# plot the AA_TOTAL by month 
iid.plot <- ggplot(df, aes(x= location_code, y=AA_TOTAL))+
  geom_point()
 #geom_smooth(method="gam",formula=y~s(x,bs="cs",k=4), method.args=list(family=poisson))+geom_point(alpha=0.1)

iid.plot 

# use inlatools to simulate different sigmas for the normal prior of iid
iid.1 <-inlatools::simulate_iid(sigma=0.1)

plot(iid.1,link="log")

iid.2 <-inlatools::simulate_iid(sigma=1)

plot(iid.2,link="log")

iid.3 <-inlatools::simulate_iid(sigma=3)

plot(iid.3,link="log")
```

```{r list of iid priors}

priors.iid <- list(
prior.iid.1 <- list(prior="pc.prec",param=c(0.1,0.05)),#per simulations
prior.iid.2 <- list(prior="pc.prec",param=c(1,0.05)), #per simulations
prior.iid.3 <- list(prior="pc.prec",param=c(3,0.05))  #per simulations
)

priors.iid.names.vector <-  c("iid.1", "iid.2", "iid.3")
```


```{r m.t.iid}

m.t.iid <- lapply(priors.iid, function(x) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(g20_day.max= df[["g20_day.max"]], 
                     location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max +
  f(location_code, model ="iid" ,
   hyper=list( theta= x #list(prior="pc.prec",param=c(0.1,0.05))
                      #list(prior="pc.prec",param=c(1,0.05))
               ) ) +
  f(month, model ="rw1")+
  f(spatial.field, model = spde)

  
m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )


})



m.t.iid.names <- fx.prior.names(m.t.iid,"time", priors.iid.names.vector)

```

```{r m.s.iid}

m.s.iid <- lapply(priors.iid, function(x) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(i_total= df[["i_total"]], 
                  g20_day.max= df[["g20_day.max"]],
                  location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                

  formula <- y ~ -1 + Intercept + g20_day.max + i_total +
f(location_code, model ="iid" ,
   hyper=list( theta= x #list(prior="pc.prec",param=c(0.1,0.05))
                      #list(prior="pc.prec",param=c(1,0.05))
               ) ) +
  f(month, model ="rw1")+
  f(spatial.field, model = spde)


m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T)
           )

})

m.s.iid.names <- fx.prior.names(m.s.iid,"space", priors.iid.names.vector)

```

## fixed effects 
We assumed zero- mean Gaussian prior distributions $\beta \sim Normal(0,1000)$ for all fixed effects

### prior for the fixed effect of spraying house i at time t using g20
```{r simulate fe.g20, eval=FALSE}

# plot the AA_TOTAL by month 
fe.g20.plot <- ggplot(df, aes(x= g20_day.max, y=AA_TOTAL))+
 geom_point()

fe.g20.plot 

fe.0 <- curve( dlnorm( x , 0 , 1000 ) , from=0 , to=100 , n=200 )

#the mean of a log-normal distribution is exp(μ + σ2/2)

mean.fe.0 <- 0+(1000^2/2)
#5e+05

fe.1 <- curve( dlnorm( x , 0 , 10 ) , from=0 , to=100 , n=200 )

mean.fe.1 <- 0+(10^2/2)
#50

fe.2 <- curve( dlnorm( x , 0 , 1 ) , from=0 , to=100 , n=200 )

mean.fe.2 <- 0+(1^2/2)
#0.5

fe.3 <- curve( dlnorm( x , 0 , 0.5 ) , from=0 , to=100 , n=200 )

mean.fe.3 <- 0+(0.5^2/2)
#0.125
```

```{r list of fe.g20 priors}

priors.fe.g20 <- list(
prior.fe.g20.1 <- list(
        mean= list(g20_day.max= 0),
        prec= list(g20_day.max= 10)),#per simulations
prior.fe.g20.2 <- list(
        mean= list(g20_day.max= 0),
        prec= list(g20_day.max= 1)), #per simulations
prior.fe.g20.3 <- list(
        mean= list(g20_day.max= 0),
        prec= list(g20_day.max= 0.5))) #per simulations


priors.fe.g20.names.vector <-  c("fe.g20.1", "fe.g20.2", "fe.g20.3")
```


```{r m.t.fe.g20}

m.t.fe.g20 <- lapply(priors.fe.g20, function(x) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(g20_day.max= df[["g20_day.max"]], 
                     location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                
  
formula <- y ~ -1 + Intercept + g20_day.max +
  f(location_code, model ="iid") +
  f(month, model ="rw1")+
  f(spatial.field, model = spde)

  
m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T), 
          control.fixed = x
           )


})



m.t.fe.g20.names <- fx.prior.names(m.t.fe.g20,"time", priors.fe.g20.names.vector)

```

```{r m.s.fe.g20}

m.s.fe.g20 <- lapply(priors.fe.g20, function(x) {
  
  stack <- inla.stack(
  data= list(y= list(df[["AA_TOTAL"]])), 
  
  A = list(a1,1), 
 
 
  effects= list(c(sp.index, list(Intercept= 1)),
                list(i_total= df[["i_total"]], 
                  g20_day.max= df[["g20_day.max"]],
                  location_code = df[["location_code"]], 
                     month= df[["month"]])),
                
  tag= "est")

                

  formula <- y ~ -1 + Intercept + g20_day.max + i_total +
f(location_code, model ="iid") +
  f(month, model ="rw1")+
  f(spatial.field, model = spde)


m <- inla(formula, 
           data = inla.stack.data(stack, 
                                  spde=spde), 
           family= "nbinomial",
           control.family=list(link='log'),
           control.compute = list(cpo= TRUE, dic= TRUE, waic=TRUE), 
           control.predictor = list(link=1, A= inla.stack.A(stack), 
                                    compute=T), 
          control.fixed = x
           )

})

m.s.fe.g20.names <- fx.prior.names(m.s.fe.g20,"space", priors.fe.g20.names.vector)

```


```{r output final}

m.priors<- c( m.0, m.t.spatial.names, m.s.spatial.names,
           m.t.rw1.names, m.s.rw1.names, 
           m.t.iid.names, m.s.iid.names, 

           m.t.fe.g20.names, m.s.fe.g20.names ) 

saveRDS(m.priors , here("analysis", "data", "derived_data", "model", "model_2014", "model_outputs_2014", "m.priors.14.rds"))

m.priors.fe <-  fx.fe.prior(m.priors) 
m.priors.waic <- fx.waic.prior(m.priors)

saveRDS(m.priors.fe , here("analysis", "data", "derived_data", "model", "model_2014", "model_outputs_2014", "fe.priors.14.rds"))
saveRDS(m.priors.waic, here("analysis", "data", "derived_data", "model", "model_2014", "model_outputs_2014", "waic.priors.14.rds"))
```



