---
title: "ulv_figures"
author: "Ania Kawiecki"
date: "2023-03-22"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, warning=FALSE, message=FALSE}
library(pacman)
pacman::p_load(
  tidyverse, sf, lubridate, here,
  patchwork, # allows plots to be collated
  RColorBrewer, # allows selection of plot palettes
  scales, # also allows selection of plot palettes
  ggspatial, # allows map annotation with north arrow
  ggtext, # ggtext allows the text inside ** to be displayed in italics
  latex2exp # allows equations in ggplot text
)
```



# METHODS 

## Fig. 1 


## Visual representation of the ring distance schemes 


```{r read in Fig 1 data}
# import data with all houses within a 1000m buffer of each study household
gis.buff.14 <- readRDS(here("analysis", "data", "raw_data", "gis.buff.sample.14.rds"))
# import data of houses sprayed the week before
i.bio <- readRDS(here("analysis", "data", "derived_data", "results", "i.bio.rds"))
i.100m <- readRDS(here("analysis", "data", "derived_data", "results", "i.100m.rds"))
# import ring data
i.buffer.bio <- readRDS(here("analysis", "data", "derived_data", "results", "i.buffer.bio.rds"))
i.buffer.100m <- readRDS(here("analysis", "data", "derived_data", "results", "i.buffer.100m.rds"))

# extract the study data frame from the data frame that includes all houses within a 1000m buffer of each study household
study.data <- gis.buff.14 %>%
  filter(!is.na(exp)) %>%
  select(c(
    "location_code", "date", "cycle_1", "cycle_2", "cycle_3", "cycle_4",
    "cycle_5", "cycle_6", "exp", "zone", "geometry"
  ))

# choose one of the households to represent household i
i <- study.data[which(study.data$location_code == "HTB803" & study.data$date == "2014-04-14"), ]
```

```{r plot bio rings }
buffer.bio <- ggplot() +
  geom_sf(
    data = i.bio,
    aes(colour = spray.past.w),
    size = 0.5,
    alpha = 1
  ) +
  geom_sf(
    data = i,
    colour = "red",
    size = 0.5,
    alpha = 1
  ) +
  geom_sf(
    data = i.buffer.bio,
    aes(fill = ring),
    alpha = 0.5
  ) +
  annotation_scale(location = "bl", width_hint = 0.3) +
  annotation_north_arrow(
    location = "bl", which_north = "true",
    pad_x = unit(0.0, "in"), pad_y = unit(0.2, "in"),
    style = north_arrow_fancy_orienteering
  ) +
  scale_fill_brewer(
    palette = "YlOrRd",
    direction = 1,
    name = "Distance ring (m)"
  ) +
  scale_color_brewer(
    palette = "Dark2",
    direction = 1,
    name = "House sprayed \nin previous week"
  ) +
  coord_sf(xlim = c(692457.9, 694457.9), ylim = c(9585375, 9587375)) +
  theme_bw(
    base_size = 12,
    base_family = "Arial"
  )

buffer.bio
```



```{r plot 100m rings }
buffer.100m <- ggplot() +
  geom_sf(
    data = i.100m,
    aes(colour = spray.past.w),
    size = 0.5,
    alpha = 1
  ) +
  geom_sf(
    data = i,
    colour = "red",
    size = 0.5,
    alpha = 1
  ) +
  geom_sf(
    data = i.buffer.100m,
    aes(fill = ring),
    alpha = 0.5
  ) +
  annotation_scale(location = "bl", width_hint = 0.3) +
  annotation_north_arrow(
    location = "bl", which_north = "true",
    pad_x = unit(0.0, "in"), pad_y = unit(0.2, "in"),
    style = north_arrow_fancy_orienteering
  ) +
  scale_fill_brewer(
    palette = "YlOrRd",
    direction = 1,
    name = "Distance ring (m)"
  ) +
  scale_color_brewer(
    palette = "Dark2",
    direction = 1,
    name = "House sprayed \nin previous week"
  ) +
  coord_sf(xlim = c(692457.9, 694457.9), ylim = c(9585375, 9587375)) +
  theme_bw(
    base_size = 12,
    base_family = "Arial"
  )

buffer.100m
```

```{r Fig 1 distance rings}
# combine both plots using patchwork::
buffer.rings <- buffer.bio / buffer.100m +
  plot_annotation(
    title = "Figure 1",
    tag_levels = "A"
  )

ggsave(
  filename = "fig1.jpg", buffer.rings,
  width = 150, height = 160, dpi = 500, units = "mm"
)
```

# RESULTS


##  Fig.2 Effects of sprays within households

```{r read in Fig 2 data }
curves.model.time <- readRDS(here("analysis", "data", "derived_data", "results", "curves.model.time.rds"))

# read in model outputs modified for both time and space weighted models
waic.time <- readRDS(here("analysis", "data", "derived_data", "results", "waic.time.rds"))
```


### Fig 2 A
Relative model fits of within-household temporal weighting functions for spray effects. Thicker red lines indicate best-fitting models, with the thickest line indicating the best-fitting model and the other thick lines representing models where the WAIC was not significantly different from the WAIC of the best fitting model

```{r Fig 2 A}
# plot decay curves for the within-household models, color coded by dWAIC

p.curves.dwaic <- ggplot(curves.model.time, aes(x = days, y = y, group = curve)) +
  geom_line(aes(
    color = rank_waic, # color of the decay curves by rank WAIC of the model including the variable that used that decay function
    size = waic.difference.from.best.model # size of the line indicates if the dWAIC was significantly different from the lowest WAIC value
  )) +
  # lower (better) WAIC rank values are red, higher (worse) ranks are blue
  scale_colour_gradient2(
    low = "red",
    mid = "grey",
    high = "blue",
    midpoint = 35
  ) +
  # size of the curve lines indicate if the dWAIC was significantly different from the lowest WAIC value
  scale_size_manual(values = c(`Best model` = 2, `No significant difference` = 1.5, `Significant difference` = 0.5)) +
  # results from each experiment are divided by columns
  # results from models using the cumulative weight of all previous sprays vs the weight of the most recent spray are divided by rows
  facet_grid(spray.effect.weight.type ~ experiment,
    # allow for thicker facet label to fit the text
    labeller = labeller(spray.effect.weight.type = label_wrap_gen(width = 20))
  ) +
  ylim(0, 1) +
  labs( # define labels for legens and axis
    y = "Relative weight of the spray effect", x = "Days since spray event",
    colour = "WAIC rank",
    # \n adds a line break
    size = "WAIC difference \nfrom best model"
  ) +
  theme_bw(
    # per journal requirements establish font and font size
    base_size = 12,
    base_family = "Arial"
  ) +
  # customize the size legend to have 3 rows
  guides(size = guide_legend(nrow = 3))
```

### Fig 2 B
Decay functions applied to the days since most recent spray that were within the top five best-fitting models by average WAIC rank across the two experiments.
```{r Fig 2 B}
waic.both.5 <- waic.time %>%
  filter(avg_rank_waic %in% avg_rank_waic_top5) %>%
  # consensus.model= identifies m_best as the best-fitting model from the within-household spray effects model comparison
  mutate(consensus.model = case_when(
    spray.effect == "Gaussian 20 Most recent spray" ~ "Consensus model",
    TRUE ~ "Top 5"
  )) %>%
  select(c("spray.effect", "spray.effect.type", "avg.rank.waic", "consensus.model")) %>%
  distinct()


curves.both.5 <- waic.both.5 %>%
  # join to the data set that provides data for plotting the decay curve lines
  left_join(
    curves.model.time[, c("spray.effect", "experiment", "days", "y", "decay", "curve")] %>%
      select(-c("experiment")) %>%
      distinct(),
    by = c("spray.effect")
  ) %>%
  mutate(
    curve = fct_relevel(curve, c("k=0.04", "k=0.06", "sigma=15", "sigma=20", "sigma=25")),
    decay = fct_relevel(decay, c("Gaussian", "Exponential"))
  )

# assign different color palettes to the k values and the sigma values
color.k.both <- hue_pal(h = c(100, 250))(2)
color.g.both <- hue_pal(h = c(0, 50))(3)

# this vector is a list of colors for each varying parameter in the top 5 models
time.decay.both <- c(color.k.both, c("#FF6C91", "red", "#D98F00"))

p.curves.both.5 <- ggplot(curves.both.5, aes(x = days, y = y, group = curve)) +
  geom_line(aes(
    color = curve, # color defines the varying parameter (k or sigma) of the decay function used for that model's spray effect weight
    linetype = decay, # different line pattern to distinguish exponential from Gaussian decay functions
    size = consensus.model # size of the line indicates if the line corresponds to the selected consensus model or not
  )) +
  # add manual labels for the varying parameters
  scale_color_manual(
    labels = parse(text = c("k==0.04", "k==0.06", "sigma==15", "sigma==20", "sigma==25", "sigma==30")),
    # assign the selected colors to these values
    values = time.decay.both
  ) +
  # assign sizes
  scale_size_manual(values = c(`Consensus model` = 2, `Top 5` = 1)) +
  ylim(0, 1) +
  labs( # add informative labels to the legends and axes
    y = "Relative weight of the spray effect", x = "Days since spray event",
    colour = "Varying parameter",
    linetype = "Decay function",
    size = "Average WAIC rank"
  ) +
  theme_bw(
    base_size = 12, # per journal requirements establish font and font size
    base_family = "Arial"
  ) +
  # left align text in legend
  theme(legend.text.align = 0)

p.curves.both.5
```
Using the sample data this code actually produces no curves, because the best average rank models do not have decay values. 

```{r Fig 2 together}
# collate fig 2 A and B
fig2 <- (p.curves.dwaic / p.curves.both.5) +
  plot_annotation(
    title = "Figure 2",
    # add labels A and B to the top left corner
    tag_levels = "A"
  )

ggsave(
  filename = "fig2.jpg", fig2,
  width = 170, height = 225, dpi = 500, units = "mm"
)
```


## Fig. 3  % reduction for *Ae. Aegypti* abundance following sprays

```{r read fig 3 data}
# import calculated reduction in Ae. aegypti over time
mg20.14.red <- readRDS(here("analysis", "data", "derived_data", "results", "mg20.14.red.rds"))
```


```{r fig 3 reduction}
plot.mg20.14.red <- ggplot(mg20.14.red, aes(x = days, y = reduction)) +
  # add 95% CI area around the mean line
  geom_ribbon(
    data = mg20.14.red, aes(
      ymin = u.red,
      ymax = l.red
    ),
    alpha = 0.2
  ) +
  # add mean line
  geom_line(data = mg20.14.red) +
  # add meaningful labels
  labs(
    title = "Figure 3",
    y = TeX(r"(Reduction of *Ae.aegypti* vs. no-spray baseline (%))"), # use of TeX(r" ") allows italics and equations in the label text
    x = "Days since most recent spray event"
  ) +
  xlim(0, 60) +
  scale_y_reverse(limits = c(100, -15)) +
  annotate("text",
    x = 30, y = 75,
    label = TeX(
      r"($Reduction = 1 - RR = 1 - e^{-0.99 \times e^{\frac{- days^2}{2 \times 20^2}}})" # add text with the model equation
    )
  ) +
  theme_bw(
    base_size = 12, # per journal requirements establish font and font size
    base_family = "Arial"
  ) +
  # left align text in legend
  theme(
    legend.text.align = 0,
    axis.title.y = ggtext::element_markdown()
  )

plot.mg20.14.red

ggsave(
  filename = "fig3.jpg", plot.mg20.14.red,
  width = 85, height = 100, dpi = 500, units = "mm"
)
```
